MRD_final_microbiome

### 2019-06-19 GlobalMicrobiome_NS.Rmd
updated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/globalmicrobiome')

#test
```

@@

# samples x species as input
library(vegan)
permanova <- adonis(t(otu) ~ mnd,
               data = meta, permutations=999, method = "bray")

# P-value
print(as.data.frame(permanova$aov.tab)["mnd", "Pr(>F)"])
summary(permanova$aov.tab)
```

Check that variance homogeneity assumptions hold (to ensure the reliability of the results):Check that variance homogeneity assumptions hold (to ensure the reliability of the results):
```{r ANOVA}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/globalmicrobiome')
# test
#test
```

@@

# samples x species as input
library(vegan)

# MND
mnd.permanova <- adonis(t(mnd.otu) ~ mnd,
               data = meta, permutations=999, method = "bray")
# P-value
print(as.data.frame(mnd.permanova$aov.tab)["mnd", "Pr(>F)"])
summary(mnd.permanova$aov.tab)

# PD
pd.permanova <- adonis(t(pd.otu) ~ pd,
               data = meta, permutations=999, method = "bray")
# P-value
print(as.data.frame(pd.permanova$aov.tab)["pd", "Pr(>F)"])
summary(pd.permanova$aov.tab)

# AD
ad.permanova <- adonis(t(ad.otu) ~ ad,
               data = meta, permutations=999, method = "bray")
# P-value
print(as.data.frame(ad.permanova$aov.tab)["ad", "Pr(>F)"])
summary(ad.permanova$aov.tab)

Check that variance homogeneity assumptions hold (to ensure the reliability of the results):Check that variance homogeneity assumptions hold (to ensure the reliability of the results):
```{r ANOVA}
#MND
mnd.dist <- vegdist(t(mnd.otu))
mnd.anov <- anova(betadisper(mnd.dist, meta$mnd))
summary(mnd.anov)
tidy(mnd.anov)

#PD
pd.dist <- vegdist(t(pd.otu))
pd.anov <- anova(betadisper(pd.dist, meta$pd))
summary(pd.anov)
tidy(pd.anov)

#AD
ad.dist <- vegdist(t(ad.otu))
ad.anov <- anova(betadisper(ad.dist, meta$ad))
summary(ad.anov)
tidy(ad.anov)
